\bf Nonparametric Block Bootstrap Kolmogorov-Smirnov Goodness-of-Fit Test

### 2025-05-30 manuscript/manuscript.tex
fixed plots still need to finish reply letter

Even for the settings with block sizes that are typically less than
$\sqrt{n}$ such as for $n = 800, X_i \sim N(8, 8)$, and $\tau = 0.5$, our 
algorithm still does not hold its size as demonstrated in 
Figure~\ref{fig:my_setting}, and the block
sizes are still much larger than $l = \lceil n^{1/3} \rceil$, which is often
considered optimal in general.

\begin{figure}[tbp]
  \centering
  \includegraphics[scale=1]{figures/my_setting}
  \caption{Q-Q plot of the p-values testing that a length-800 time series with
    Kendall's $\tau = 0.5$
    have marginal normal distribution with true data generating distribution
    being $N(8,8)$.
  }
  \label{fig:my_setting}
\end{figure}

\begin{figure}[tbp]
  \centering
  \includegraphics[scale=1]{figures/block_dist}
  \caption{Distribution of the selected block sizes using
  \citet{politis2004automatic}'s procedure applied to a length-800 time series with
    Kendall's $\tau = 0.5$ data generating distribution $N(8,8)$.
  }
  \label{fig:block_dist}
\end{figure}

@@

\item[Data availability statement:] The data and code used in the real data analysis and simulation
studies are publicly available in a GitHub repo:
\url{https://github.com/mathewchandy03/Bootstrap_KS_Test}.

>>>>

Even for settings where the block sizes are usually less than $\sqrt{n}$ -
such as for $n = 800$, $\tau = 0.5$, and $X_i \sim N(8, 8)$ - the 
block
sizes are almost always larger than $l = \lceil n^{1/3} \rceil$.

\begin{figure}[tbp]
  \centering
  \includegraphics[scale=1]{figures/block_dist}
  \caption{Distribution of the selected block sizes using
  \citet{politis2004automatic}'s procedure applied to 20000 length-800 time 
  series with
    Kendall's $\tau = 0.5$ data generating distribution $N(8,8)$.
  }
  \label{fig:block_dist}
\end{figure}

Despite this, our 
algorithm holds its size somewhat well for moderately dependent
series as demonstrated in 
Figures~\ref{fig:alt_normal} and \ref{fig:alt_gamma}. Both 
\citet{politis2004automatic}'s setting and the cubic root setting result
in the method not holding its size for $|\tau| > 0.5$. 
Figure~\ref{fig:alt_rr} also shows that the two setting are comparably
powerful for $|\tau| <= 0.5$. However, we still
recommend the cubic root setting over that introduced by 
\citet{politis2004automatic} because the latter fails to hold its size
for negative $\tau$, particularly for smaller sample sizes. It is important to 
note that another block size selection rationale could yield better results.

\begin{figure}[tbp]
  \centering
  \includegraphics[scale=1]{figures/alt_normal}
  \caption{Q-Q plots of the p-values testing that a time series
    have marginal normal distribution with true data generating distribution
    being $N(8,8)$, when using \citet{politis2004automatic}'s procedure
    to select block sizes.
  }
  \label{fig:alt_normal}
\end{figure}

\begin{figure}[tbp]
  \centering
  \includegraphics[scale=1]{figures/alt_gamma}
  \caption{Q-Q plots of the p-values testing that a time series
    have marginal gamma distribution with true data generating distribution
    being $\Gamma(8,1)$, when using \citet{politis2004automatic}'s procedure
    to select block sizes.
  }
  \label{fig:alt_gamma}
\end{figure}

\begin{figure}[tbp]
  \centering
  \includegraphics[scale=1]{figures/alt_rr}
  \caption{Empirical power curve as a function of $\tau$ for
    $n \in \{100, 200, 400, 800\}$ and true marginal distribution
    $\in \{N(8,8), \Gamma(8,1)\}$, when using \citet{politis2004automatic}'s 
    procedure
    to select block sizes. When the data was generated from $N(8,8)$,
    we tested for the gamma family. When the data was generated from
    $\Gamma(8,1)$, we tested for the normal family.
  }
  \label{fig:alt_rr}
\end{figure}

@@

\item[Data availability statement:] The data and code used in the real data analysis and simulation studies are publicly available in a GitHub repo:

\url{https://github.com/mathewchandy03/Bootstrap_KS_Test}.

### 2025-05-30 manuscript/reply.tex
fixed plots still need to finish reply letter

@@

@@

\begin{comment}
2. The work presented here is useful, however I have believe the explanations
for the correction term may need modification. Here the entire justification is
based on the null case which does not cover the case when the null is not true.
Justification for the correction term in \citet{babu2004goodness} is not based 
on just the
null case. The same seems to be true here, and in that case, Section 2 needs
rewriting.
\end{comment}

>>>>

\begin{comment}
This manuscript proposes a nonparametric block bootstrap (NPBB) method for applying the

Kolmogorov-Smirnov (KS) test to stationary time series data with unknown parameters and un-
specified serial dependence. The authors claim that the method offers a robust nonparametric

solution for evaluating the fit of marginal distributions when data are serially dependent, without
requiring assumptions about the form of this dependence. The paper is well-written and smooth
to read. However, upon review, I find that it lacks methodological and theoretical innovation.
\end{comment}

@@

\begin{comment}
This paper focuses on approximating the distribution of the Kolmogorov-
Smirnov (KS) statistic for stationary time series. SpeciÖcally, it deals with the

distribution of KS statistic for testing if the marginal distribution belongs to
a speciÖed parametric family. Parametric bootstrap requires knowledge of the

nature of serial dependence, and for this reason, nonparametric bootstrap is em-
plyed here. For the iid case, \citet{babu2004goodness} obtained a correction term

so that the corrected bootstraped statistic can be used to approximate distribu-
tion of the KS statistic. This paper does the same except it uses nonparametric

bootstrap developed by Kunsch and others. Finally the author(s) present some
empirical work in support of their proposed procedure. Simulations indicate

that the proposed procedure may work for large samples and moderate depen-
dence.
\end{comment}

@@

\begin{comment}
2. The work presented here is useful, however I have believe the explanations
for the correction term may need modification. Here the entire justification is
based on the null case which does not cover the case when the null is not true.
Justification for the correction term in \citet{babu2004goodness} is not based 
on just the
null case. The same seems to be true here, and in that case, Section 2 needs
rewriting.

\mc{I will insert the rest of the comment here}
\end{comment}
